% For LaTeX-Box: root = syllabus_stat105_F15.tex 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  File Name: syllabus_stat105_F15.tex
%  Purpose:
%
%  Creation Date: 24-08-2015
%  Last Modified: Tue Aug 22 03:31:41 2017
%  Created By:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset  -.85in

\pagestyle{empty}

%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\begin{center}
{\bf Statistics 430 \ \ TR 2:10 - 3:30 PM, Lagomarcino Hall W0272}
\end{center}
\centerline{\textbf{Empirical Methods for the Computer Sciences}}

\setlength{\unitlength}{1in}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}

\renewcommand{\arraystretch}{2}
 
\vskip.25in
\noindent\textbf{Instructor:} Ian Mouzon (imouzon@iastate.edu, Snedecor Hall 3220, 1-515-294-7891)
\vskip.25in
\noindent\textbf{TA:} Haijuan Zhang (haijuan@iastate.edu)
\vskip.25in
\noindent\textbf{Office Hours:} TR 9:30-10:30 AM, 3:30-4:30 PM in Snedecor Hall 3220. 
%\footnoteremark
%\footnotetext{
%I try to make sure that students who would like to attend office hours have that ability. If none of these times fit your course schedule, additional office hours can be arranged.
%You can also ask questions through emails at any time - I check my email frequently and emails will generally be answered within 24 hours (except on weekends). 
%However, I may not respond immediately – so it is in your best interest not to wait until the last minute before homework deadlines or exams.
%}
\vskip.25in
\noindent\textbf{TA Office Hours:} \textit{TBD}
\vskip.25in
\noindent\textbf{Web:} https://imouzon.github.io/stat430, Blackboard (https://bb.its.iastate.edu/)
\vskip.25in
\noindent\textbf{Course Description:}
\textit{(Prereq: STAT 330 or an equivalent course, MATH 166, knowledge of linear algebra.)}
Statistical methods for research involving computers; exploratory data analysis; selected topics from analysis of designed experiments - analysis of variance, hypothesis testing, interaction among variables; linear regression, logistic regression, Poisson regression; parameter estimation, prediction, confidence regions, dimension reduction techniques, model diagnostics and sensitivity analysis; Markov chains and processes; simulation techniques and bootstrap methods; applications to computer science, bioinformatics, computer engineering - programs, models and systems as objects of empirical study; communicating results of empirical studies. Statistical software: R.
\vskip.25in
\noindent\textbf{Textbook:}  
\textit{Mathematical Statistics and Data Analysis} (ISBN 978-0534399429) by John A. Rice.
\vskip.25in
\noindent\textbf{Important Dates}:
\begin{center} \begin{minipage}{5in}
\begin{flushleft}
Drop Deadline \dotfill October 27th\\
Thanksgiving break \dotfill November 20th - 24th\\
   First Exam \textit{(tentative)} \dotfill September 26th\\
Second Exam  \textit{(tentative)} \dotfill November 6th\\
   Course Final \dotfill December 15th, 9:45-11:45 AM (Friday)\\
\end{flushleft}
\end{minipage}
\end{center}
\vskip.25in
\noindent\textbf{Assessment Policy:} Grades (include plus/minus) will be determined based on the following:
\begin{center} 
\begin{minipage}{6.5in}
\begin{flushleft}
\textbf{Exams:} 
There will be two semester exams and a comprehensive final. The semester exams will be given during the lecture period and will be closed book. The final exam is comprehensive and is scheduled for Friday, 12/15 from 9:45 - 11:45 AM.
\end{flushleft}
\end{minipage}
\end{center}
\begin{center} 
\begin{minipage}{6.5in}
\begin{flushleft}
\textbf{Homework:} 
Most weeks, homework will be assigned and to be collected the following week in class. To accomodate unexpected events that may impact students ability to complete this assignments on time I will drop the lowest of the homework grades from the overall average. However, deadlines should be on all assignments.\\
\vskip.25in
The components have the following weights:\\
\vskip.25in
\begin{center} 
\begin{minipage}{6in}
\begin{flushleft}
\textbf{Exam 1} \dotfill 15\% (09/26, in class) \\
\textbf{Exam 2} \dotfill 15\% (11/06, in class) \\
\textbf{Homework:} \dotfill 30\%  (assigned weekly) \\
\textbf{Course Project:} \dotfill 20\% (details to follow) \\
\textbf{Final Exam:} \dotfill 20\% (12/15, 9:45-11:45, location TBD) \\
\end{flushleft}
\end{minipage}
\end{center}
\end{flushleft}
\end{minipage}
\end{center}

% \noindent\textbf{Course Outline:} 
% \begin{center} \begin{minipage}{6.5in}
% \begin{flushleft}
% Introduction, Data Collection (Ch.1, 2) \dotfill HW1 assigned\\
% Descriptive Statistics (sec. 3.1 3.2)  \dotfill HW1 due, HW2 assigned\\
% Descriptive Statistics, Line Fitting  (Ch. 3.3, 4.1, 4.2) \dotfill HW2 due, HW3 assigned\\
% Curve and Surface Fitting (sec. 4.2) \dotfill HW3 due, HW4 assigned \\
% Random Variables (sec. 5.1) \dotfill HW4 due, HW5 assigned \\
% Random Variables (sec. 5.1) \dotfill \textbf{Exam 1}, covering Ch. 1 - 4 \\
% Random Variables (sec. 5.2) \dotfill HW5 due, HW6 assigned  \\
% Random Variables (sec. 5.2) \dotfill HW6 due, HW7 assigned  \\
% Random Variables (sec. 5.4, 5.5) \dotfill No homework assigned\\
% Random Variables, Simple Inference (sec. 5.5, 6.1) \dotfill HW7 due, HW8 assigned \\
% Simple Inference (6.1) \dotfill \textbf{Exam 2}, covering Ch. 5 \\
% Simple Inference (6.2, 6.3) \dotfill HW8 due, HW9 assigned  \\
% Simple Inference (6.3, 6.6) \dotfill No homework assigned\\
% Thanksgiving break \dotfill No homework assigned \\
% One Way Model CI's for Linear Functions of Means (7.1, 7.2) \dotfill HW9 due, HW10 assigned  \\
% One Way ANOVA, Control Charts, Review (7.4, 7.5) \dotfill HW10 due \\
% \textbf{Final Exam} \dotfill 12/15, location to be announced.
% \end{flushleft}
% \end{minipage}
% \end{center}

\vskip.25in
\noindent\textbf{Attendance}:  
Grades do not directly depend on attendance - still, experience shows that attendance and course performance are significantly related to each other. In order to get the most out of this course and do his or her personal best, it is necessary for a student to treat attendance as if it were mandatory.

\vskip.25in
\noindent\textbf{Academic Honesty}:  
As an Iowa State University student, you have agreed to abide by the University's academic honesty policy (http://www.dso.iastate.edu/ja/academic/misconduct.html).
Academic misconduct is a serious matter and student's suspected of academic dishonesty will be reported to the Dean of Students Office.
Questions related to course assignments and the academic honesty policy should be directed to the instructor.

\vskip.25in
\noindent\textbf{Extra Help}:  
Do not hesitate to come to my office during office hours or schedule an appointment to discuss a homework problem or any aspect of the course. If you want to hire an outsider tutor (i.e., for a fee), you can find a list of such people through the stat department.

\vskip.25in
\noindent\textbf{Disability Accommodation}:  
Iowa State University complies with the Americans with Disabilities Act and Sect 504 of the Rehabilitation Act. If you have a disability and anticipate needing accommodations in this course, please contact your instructor (in this case, Ian Mouzon) to set up a meeting within the first two weeks of the semester or as soon as you become aware of your need. Before meeting with the instructor, you will need to obtain a SAAR form with recommendations for accommodations from the Disability Resources Office, located in Room 1076 on the main floor of the Student Services Building. Their telephone number is 515-294-7220 or email disabilityresources@iastate.edu. Retroactive requests for accommodations will not be honored.

\vskip.25in
\noindent\textbf{Dead Week}:
This class follows the Iowa State University Dead Week policy as noted in section 10.6.4 of the Faculty Handbook http://www.provost.iastate.edu/resources/faculty-handbook .

\vskip.25in
\noindent\textbf{Harassment and Discrimination}:
Iowa State University strives to maintain our campus as a place of work and study for faculty, staff, and students that is free of all forms of prohibited discrimination and harassment based upon race, ethnicity, sex (including sexual assault), pregnancy, color, religion, national origin, physical or mental disability, age, marital status, sexual orientation, gender identity, genetic information, or status as a U.S. veteran. Any student who has concerns about such behavior should contact his/her instructor, Student Assistance at 515-294-1020 or email dso-sas@iastate.edu, or the Office of Equal Opportunity and Compliance at 515-294-7612.

\vskip.25in
\noindent\textbf{Religious Accommodation}:
If an academic or work requirement conflicts with your religious practices and/or observances, you may request reasonable accommodations. Your request must be in writing, and your instructor or supervisor will review the request.  You or your instructor may also seek assistance from the Dean of Students Office or the Office of Equal Opportunity and Compliance.

\vskip.25in
\noindent\textbf{Contact Information}:
If you are experiencing, or have experienced, a problem with any of the above issues, email academicissues@iastate.edu.

\end{document}
