<!DOCTYPE html>
<html>
   <head>
      <link href ="../global/www/css/stat105.css" type="text/css" rel = "stylesheet">
      <style type="text/css">
      @import url(https://fonts.googleapis.com/css?family=Droid+Serif:400,700,400italic);
      @import url(https://fonts.googleapis.com/css?family=Yanone+Kaffeesatz);
      @import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);
      </style>

      <title>STAT 105: Lecture 7</title>
      <meta http-equiv="Content-Type" content="text/html; charset=UTF-8"/>
      <meta name="keywords" content="statistics,engineering,stat105,iastate"/>
      <meta name="description" content="Lecture 7: Graphs, etc."/>
   </head>

   <body>
   <textarea id="source">

```{r cache=FALSE, echo=FALSE, include = FALSE}
   library(usefulR)
   library(ggplot2)
   library(knitr)

   knitrSetup(flavor = "html", fig.folder = "www/lecture7", cache.folder = "www/lecture7")

   if(FALSE) 
      usefulR::rmd2html("lecture7.Rmd")

   mode_values <- function(x){
      tbl <- table(x)
      names(which(tbl == max(tbl)))
   }

   print_multiple <- function(x){
      if(length(x) == 1){
         x
      }else{
         xfirst <- x[1:(length(x)-1)]
         paste(paste0(xfirst,collapse = ", "),"and",x[length(x)])
      }
   }

   my_quantile <- function(p,x){
      x <- x[order(x)]
      
      n <- length(x)

      raw.i <- n*p + .5
      floor.i <- floor(raw.i)
      if(floor.i == raw.i){
         x[floor.i]
      }else{
         x[floor.i] + (n*p - floor.i + .5)*(x[floor.i+1] - x[floor.i])
      }
   }

   set.seed(1999)

```
name: inverse
layout: true
class: center, middle, inverse
---
# STAT 105: Lecture 7
## Chapter 4: Describing Relationships Between Variables
.footnote[Course page: [imouzon.github.io/stat105](https://imouzon.github.io/stat105)]
---
# Recap
## Quantiles and Their Plots
---
layout:false
.left-column[
## Recap
### `\(Q(p)\)`
]
.right-column[
### Two useful pieces of notation:

**floor**: `\(\lfloor x \rfloor \)` is the largest integer smaller than or equal to `\( x \)`

**ceiling**: `\(\lceil x \rceil \)` is the smallest integer larger than or equal to `\( x \)`

### The Quantile Function

For a data set consisting of `\(n\)` values that when ordered are `\(x_1 \le x_2 \le \ldots \le x_n\)` and `\( 0 \le p \le 1\)`.
Let `\(i = \lfloor n \cdot p + .5 \rfloor \)`.
We define the **quantile** `\(Q(p)\)` as:

<span style = "font-size: 70%">
`\[
   Q(p) = 
   \begin{cases}
   x_i & \lfloor n \cdot p + .5 \rfloor = n \cdot p + .5 \\
   x_i  + \left( n p - i + .5 \right) \left( x_{i+1} - x_i \right) &  \lfloor n \cdot p + .5 \rfloor \ne n \cdot p + .5 \\
   \end{cases}
\]`
</span>

Basically
-  if `\(n \cdot p + .5\)` is an integer, we are going to use an `\(x_i\)` from our sample.
-  if `\(n \cdot p + .5\)` is **not** an integer, we add a little bit
]
---
layout:false
.left-column[
## Recap from Lecture 6
### `\(Q(p)\)`
]
.right-column[

```{r include = FALSE}
newsamp <- c(8, 19, 34, 57, 109)
newsamp_ord <- newsamp[order(newsamp)]

quantiles <- c(.1,.17,.25,.3,.5,.6,.7,.9)
```
**Example**
Using the quantile function , find the .10, .17, .25, .30, .50, .70, and .90 quantiles for the sample:
<center>
`r newsamp`
</center>

**Solution**

| `\(p\)`  | .10 | .17 | .25 | .30 | .50 | .70 | .90 |
|----------|-----|-----|-----|-----|-----|-----|-----|
| `\(n \cdot p + 0.5\)`  |     |     |     |     |     |     |     |
| `\(i\)`  |     |     |     |     |     |     |     |
| `\(Q(p)\)`  |     |     |     |     |     |     |     |

1.  Start with a simple table
]
---
layout:false
.left-column[
## Recap
### `\(Q(p)\)`
]
.right-column[

**Example**
Using the quantile function , find the .10, .17, .25, .30, .50, .70, and .90 quantiles for the sample:
<center>
`r newsamp`
</center>

**Solution**

| `\(p\)`  | .10 | .17 | .25 | .30 | .50 | .70 | .90 |
|----------|-----|-----|-----|-----|-----|-----|-----|
| `\(n \cdot p + 0.5\)`  | `r 5*.10 + .5` | `r 5*.17 + .5` | `r 5*.25 + .5` | `r 5*.30 + .5` | `r 5*.50 + .5` | `r 5*.70 + .5` | `r 5*.90 + .5` |
| `\(i\)`  | `r floor(5*.10 + .5)` | `r floor(5*.17 + .5)` | `r floor(5*.25 + .5)` | `r floor(5*.30 + .5)` | `r 5*.50 + .5` | `r floor(5*.70 + .5)` | `r floor(5*.90 + .5)` |
| `\(Q(p)\)`  |     |     |     |     |     |     |     |

1.  Start with a simple table
2.  Find all the values of `\(n \cdot p + 0.5\)` and `\(i = \lfloor n \cdot p + 0.5 \rfloor\)`
]
---
layout:false
.left-column[
## Recap
### `\(Q(p)\)`
]
.right-column[

**Example**
Using the quantile function , find the .10, .17, .25, .30, .50, .70, and .90 quantiles for the sample:
<center>
`r newsamp`
</center>

**Solution**

| `\(p\)`  | .10 | .17 | .25 | .30 | .50 | .70 | .90 |
|----------|-----|-----|-----|-----|-----|-----|-----|
| `\(n \cdot p + 0.5\)`  | `r 5*.10 + .5` | `r 5*.17 + .5` | `r 5*.25 + .5` | `r 5*.30 + .5` | `r 5*.50 + .5` | `r 5*.70 + .5` | `r 5*.90 + .5` |
| `\(i\)`  | `r floor(5*.10 + .5)` | `r floor(5*.17 + .5)` | `r floor(5*.25 + .5)` | `r floor(5*.30 + .5)` | `r 5*.50 + .5` | `r floor(5*.70 + .5)` | `r floor(5*.90 + .5)` |
| `\(Q(p)\)`  | `r my_quantile(.10,newsamp)` |  |  | `r my_quantile(.30,newsamp)` | `r my_quantile(.50,newsamp)` | `r my_quantile(.70,newsamp)` | `r my_quantile(.90,newsamp)` |

1.  Start with a simple table
2.  Find all the values of `\(n \cdot p + 0.5\)` and `\(i = \lfloor n \cdot p + 0.5 \rfloor\)`
3.  If `\(n \cdot p + 0.5 = i\)` then `\(Q(p) = x_i\)`

]
---
layout:false
.left-column[
## Recap
### `\(Q(p)\)`
]
.right-column[

**Example**
Using the quantile function , find the .10, .17, .25, .30, .50, .70, and .90 quantiles for the sample:
<center>
`r newsamp`
</center>

**Solution**

| `\(p\)`  | .10 | .17 | .25 | .30 | .50 | .70 | .90 |
|----------|-----|-----|-----|-----|-----|-----|-----|
| `\(n \cdot p + 0.5\)`  | `r 5*.10 + .5` | `r 5*.17 + .5` | `r 5*.25 + .5` | `r 5*.30 + .5` | `r 5*.50 + .5` | `r 5*.70 + .5` | `r 5*.90 + .5` |
| `\(i\)`  | `r floor(5*.10 + .5)` | `r floor(5*.17 + .5)` | `r floor(5*.25 + .5)` | `r floor(5*.30 + .5)` | `r 5*.50 + .5` | `r floor(5*.70 + .5)` | `r floor(5*.90 + .5)` |
| `\(Q(p)\)`  | `r my_quantile(.10,newsamp)` | 22.85 |  | `r my_quantile(.30,newsamp)` | `r my_quantile(.50,newsamp)` | `r my_quantile(.70,newsamp)` | `r my_quantile(.90,newsamp)` |

1.  Start with a simple table
2.  Find all the values of `\(n \cdot p + 0.5\)` and `\(i = \lfloor n \cdot p + 0.5 \rfloor\)`
3.  If `\(n \cdot p + 0.5 = i\)` then `\(Q(p) = x_i\)`
4.  Calculate the other values:

`\[
\begin{align}
Q(.17) &= x_i + (n \cdot p + 0.5)(x_{i+1} - x_i) \\\\
       &= x_1 + (5 \cdot .17 + 0.5)(x_{2} - x_1) \\\\
       &= 8 + (`r 5 * .17` + 0.5)(19 - 8) = `r 8 + (5 * .17 + 0.5)*(19 - 8)` \\\\
\end{align}
\]`

]
---
layout:false
.left-column[
## Recap
### `\(Q(p)\)`
]
.right-column[

**Example**
Using the quantile function , find the .10, .17, .25, .30, .50, .70, and .90 quantiles for the sample:
<center>
`r newsamp`
</center>

**Solution**

| `\(p\)`  | .10 | .17 | .25 | .30 | .50 | .70 | .90 |
|----------|-----|-----|-----|-----|-----|-----|-----|
| `\(n \cdot p + 0.5\)`  | `r 5*.10 + .5` | `r 5*.17 + .5` | `r 5*.25 + .5` | `r 5*.30 + .5` | `r 5*.50 + .5` | `r 5*.70 + .5` | `r 5*.90 + .5` |
| `\(i\)`  | `r floor(5*.10 + .5)` | `r floor(5*.17 + .5)` | `r floor(5*.25 + .5)` | `r floor(5*.30 + .5)` | `r 5*.50 + .5` | `r floor(5*.70 + .5)` | `r floor(5*.90 + .5)` |
| `\(Q(p)\)`  | `r my_quantile(.10,newsamp)` | 22.85 | 27.25 | `r my_quantile(.30,newsamp)` | `r my_quantile(.50,newsamp)` | `r my_quantile(.70,newsamp)` | `r my_quantile(.90,newsamp)` |

1.  Start with a simple table
2.  Find all the values of `\(n \cdot p + 0.5\)` and `\(i = \lfloor n \cdot p + 0.5 \rfloor\)`
3.  If `\(n \cdot p + 0.5 = i\)` then `\(Q(p) = x_i\)`
4.  Calculate the other values:

`\[
\begin{align}
Q(.25) &= x_i + (n \cdot p + 0.5)(x_{i+1} - x_i) \\\\
       &= x_1 + (5 \cdot .25 + 0.5)(x_{2} - x_1) \\\\
       &= 8 + (`r 5 * .25` + 0.5)(19 - 8) = `r 8 + (5 * .25 + 0.5)*(19 - 8)` \\\\
\end{align}
\]`

]
---
.left-column[
## Recap
### `\(Q(p)\)`
### Plots
]
.right-column[
### Boxplots
Use `\(Q(.25), Q(.5), Q(.75)\)` along with IQR to show spread of the data over quartiles and identify "outlying" values.

### Quantile Plots: 

Scatterplots using quatiles and their corresponding values. 

### Quantile-Quantile Plots
-  For samples of equal size `\(n\)` we can create a plot that helps us identify if the spread of the data is similar
-  We can also compare the quantiles from our sample to the quantiles of some known distribution
]

---
.left-column[
## Recap
### `\(Q(p)\)`
### Plots
]
.right-column[
### Quantile-Quantile Plots

**Example**

```{r echo = FALSE}
grp1 <- sample(30:50, 7)
grp2 <- round(3*grp1 + 2 + rnorm(7))
grp3 <- round(2*grp1 + 1 + rnorm(7,0,6))
p = (1:7 - 0.5)/7
```

-  Sample 1: `r grp1`
-  Sample 2: `r grp2`
-  Sample 3: `r grp3`
]

---
.left-column[
## Recap
### `\(Q(p)\)`
### Plots
]
.right-column[
### Quantile-Quantile Plots

**Example**

```{r echo = FALSE, cache = FALSE}
grp2 <- sample(30:50, 7)
grp3 <- round(3*grp2 + 2 + rnorm(7))
grp1 <- round(2*grp2 + 1 + rnorm(7,0,9))
p = (1:7 - 0.5)/7
```

-  Sample 1: `r grp1`
-  Sample 2: `r grp2`
-  Sample 3: `r grp3`

1. Create a table of the quantiles

| `\(p\)`  | `r round(p[1],2)`   | `r round(p[2],2)`   | `r round(p[3],2)`   | `r round(p[4],2)`   | `r round(p[5],2)`   | `r round(p[6],2)`   | `r round(p[7],2)`   |
|--|--|--|--|--|--|--|--|
| Sample 1 `\(Q(p)\)`  | `r my_quantile(p[1],grp1)`   | `r my_quantile(p[2],grp1)`   | `r my_quantile(p[3],grp1)`   | `r my_quantile(p[4],grp1)`   | `r my_quantile(p[5],grp1)`   | `r my_quantile(p[6],grp1)`   | `r my_quantile(p[7],grp1)`   |
| Sample 2 `\(Q(p)\)`  | `r my_quantile(p[1],grp2)`   | `r my_quantile(p[2],grp2)`   | `r my_quantile(p[3],grp2)`   | `r my_quantile(p[4],grp2)`   | `r my_quantile(p[5],grp2)`   | `r my_quantile(p[6],grp2)`   | `r my_quantile(p[7],grp2)`   |
| Sample 3 `\(Q(p)\)`  | `r my_quantile(p[1],grp3)`   | `r my_quantile(p[2],grp3)`   | `r my_quantile(p[3],grp3)`   | `r my_quantile(p[4],grp3)`   | `r my_quantile(p[5],grp3)`   | `r my_quantile(p[6],grp3)`   | `r my_quantile(p[7],grp3)`   |

2. Use the paired quantiles to make the plots:
```{r eval = TRUE, echo = FALSE, tidy = TRUE, fig.height = 2.7, fig.width = 2.7, dpi = 50}
   qplot(grp1,grp2, xlab = "Sample 1", ylab = "Sample 2")
   qplot(grp1,grp3, xlab = "Sample 1", ylab = "Sample 3")
   qplot(grp2,grp3, xlab = "Sample 2", ylab = "Sample 3")
```

]
---
name: inverse
layout: true
class: center, middle, inverse
---
# Chapter 4, Section 1
## Linear Relationships Between Variables
---
layout: false
# Topics covered in class (overhead):

-  Identifying possible linear relationships

-  Notation: 
   -  linear equation: `\(y \approx \beta_0 + \beta_1 x \)`
   -  fitted equation: `\(\hat{y} = b_0 + b_1 x \)`

-  Fitting lines using the principle of least squares

-  Sample correlation `\(r\)`

-  Coeffecient of determination `\(R^2\)`

-  Residuals: `\(e_i = y_i = \hat{y_i}\)`

-  **Example**: Chapter 4, Section 1, Exercise 3


</textarea>
<!-- load remark -->
<script src="https://gnab.github.io/remark/downloads/remark-latest.min.js" type="text/javascript"></script>

<!-- load mathjax -->
<script type="text/javascript" src="http://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML&delayStartupUntil=configured"></script>

<!-- Initialize (has to go in <script> tag **without** SRC attribute) -->
<script type="text/javascript">
   // Create slideshow
   var slideshow = remark.create({
      // This BREAKS MathJax: 
      // highlightLanguage: 'Python'

      // You have to tag every code block with python, like so:
      //
      // ```python
      // def add(a, b):
      //     return a + b
      // ```
   });

   // Setup MathJax
   MathJax.Hub.Config({
      tex2jax: {
         skipTags: ['script', 'noscript', 'style', 'textarea', 'pre']
      }
   });
   MathJax.Hub.Queue(function() {
      $(MathJax.Hub.getAllJax()).map(function(index, elem) {
         return(elem.SourceElement());
      }).parent().addClass('has-jax');
   });
   MathJax.Hub.Queue(function() {
      $(MathJax.Hub.getAllJax()).map(function(index, elem) {
         return(elem.SourceElement());
      }).parent().addClass('has-jax');
   });

   MathJax.Hub.Configured();
</script>
