% For LaTeX-Box: root = stat105_hw2.tex 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  File Name: stat105_hw2.tex
%  Purpose:
%
%  Creation Date: 03-09-2015
%  Last Modified: Fri Mar  4 13:47:51 2016
%  Created By:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}
\usepackage{graphicx, fancyhdr}
\usepackage{amsmath, amsfonts}
\usepackage{color}

\newcommand{\blue}[1]{{\color{blue} #1}}

\setlength{\topmargin}{-.5 in} 
\setlength{\textheight}{9 in}
\setlength{\textwidth}{6.5 in} 
\setlength{\evensidemargin}{0 in}
\setlength{\oddsidemargin}{0 in} 
\setlength{\parindent}{0 in}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}


\lhead{STAT 105, Section A} 
\chead{Homework Assignment 5} 
\rhead{Due Thursday, March 10th} 
\lfoot{Spring 2016} 
\cfoot{\thepage} 
\rfoot{} 
\renewcommand{\headrulewidth}{0.4pt} 
\renewcommand{\footrulewidth}{0.4pt} 
\newcommand{\ans}[1]{{\color{blue} \textbf{Answer: } #1}}
\renewcommand{\ans}[1]{}

\def\Exp#1#2{\ensuremath{#1\times 10^{#2}}}
\def\Case#1#2#3#4{\left\{ \begin{tabular}{cc} #1 & #2 \phantom
{\Big|} \\ #3 & #4 \phantom{\Big|} \end{tabular} \right.}

\begin{document}
\pagestyle{fancy} 

Show \textbf{all} of your work on this assignment and answer each question fully in the given context. \\

\emph{Please} staple your assignment! \\

\ben


\item 
   Consider the following scenario: I am drawing a the top card from a well shuffled deck of playing cards. After I select the top card, I make note of what the card is, and I replace it in the deck and reshuffle. I then select another card, make note of what the card is, replace it in the deck and reshuffle.

   \begin{enumerate}
      \item If I repeat this process 3 times, what is the probability that every card is the same suit?
      \item If I repeat this process 3 times, what is the probability that every card is the same rank?
      \item If I repeat this process 3 times, what is the probability that every card is the same suit and rank?
   \end{enumerate}

\item 
   Suppose that you have two fair six-sided die (meaning each side has the same chance of facing up), one red and one blue, and suppose that each roll of the pair is independent.
   Define $X$ to be the sum of the number of dots facing up on a single roll of the pair of die, and define $T$ to be the first roll of the pair of die where the sum of the dots facing up is 7.
   \begin{enumerate}
      \item Complete the following table for the random variable $X$:
         \begin{table}[h]
            \centering
            \begin{tabular}{c|c}
               $x$ & $f(x)$ \\ \hline
               1 & \\
               2 & \\
               3 & \\
               4 & \\
               5 & \\
               6 & \\
               7 & \\
               8 & \\
               9 & \\
               10 & \\
               11 & \\
               12 & \\
               13 & \\ \hline
            \end{tabular}
         \end{table}

      \item If I roll the pair of die 4 times, how many times should I expect the sum of the dots facing up on the two die to be 7? What is the probability that I roll a 7 on three of those 

      \item If I roll the pair of die 6 times, what is the probability that the sum of the dots facing up on the two die will be a 7 on three of those rolls?

      \item Find $P(T \le 5)$.

      \item Find $P(T \ge 2)$.

      \item How many times should I expect to roll the die before I see my first roll of 7. (i.e., find the \textit{expected value} of $T$).

   \end{enumerate}

\item \textbf{Chapter 5, Section 1, Exercise 1 (page 243)}

\item \textbf{Chapter 5, Section 1, Exercise 2 (page 243)}

\item \textbf{Chapter 5, Section 1, Exercise 5 (page 244)}
   
\een
\end{document}
