% For LaTeX-Box: root = stat105_F15_exam1B.tex 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  File Name: stat105_F15_exam1B.tex
%  Purpose:
%
%  Creation Date: 24-09-2015
%  Last Modified: Mon Oct  2 13:58:12 2017
%  Created By:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[addpoints]{examsetup}

\usepackage{etoolbox}
\usepackage{tikz,pgfplots}
\usepackage{graphicx, fancyhdr}
\usepackage{amsmath, amsfonts}
\usepackage{color}

%\input{stat105_exam1_info.tex}
\newcommand{\course}[1]{\ifstrempty{#1}{STAT 430}{STAT 430}}
\newcommand{\sectionNumber}{}
\newcommand{\examDate}{October 3, 2017}
\newcommand{\semester}{FALL 2017}
\newcommand{\examNumber}{I}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\examCoverPage

\begin{questions}


\question \textbf{Sets Proof} \\ For the following question, assume that $S$ is the universe, and $A$, $B$, and $C$ are subsets of $S$.

   \begin{parts}
      \part[4] Prove or disprove that $ A \cap B \subseteq A \subset A \cup B $
      \vspace{5cm}
      \part[4] Prove or disprove that if $A \not\subseteq B$ and $B \not\subseteq C$ then $A \notsubset C$.
      \vspace{5cm}
      \part[4] Prove or disprove that $(A \cap B^{c}) \cup (B \cap C^{c}) = A \cap C^{c}$
      \vspace{5cm}
   \end{parts}

\newpage

\question[8]
   Suppose that we can call a collection of sets, $\mathcal{F}$ a "sigma algebra" if 
   \begin{enumerate}
      \item $\emptyset \in \mathcal{F}$
      \item if $A \in \mathcal{F}$ then $A^{C} \in \mathcal{F}$
      \item if $A_1, A_2, \cdots \in \mathcal{F}$ then $A_1 \cup A_2 \cup \ldots \in \mathcal{F}$.
   \end{enumerate}
   Suppose that $A \cap B = \emptyset$. Write the smallest possible sigma-algebra containing $A$ and $B$.

\newpage
%-- : R code (Code in Document)
\question
Consider the following scenario: Suppose that a fair coin is tossed. If the toss results in "Heads" facing up, then a fair 6-sided die is rolled. If the toss results in a "Tails" facing up, a fair 4-sided die is rolled.

\begin{parts}
\part[2] Write the sample space of possible outcomes for this experiment, using "H\" and "T\" to denote heads and tails and integers to denote the roll of the die.
\vspace{5cm}
\part
Determine the following probabilities:
\vspace{1cm}
  \begin{subparts}
      \subpart[2] Find $P\left(\text{"the coin toss results in heads"}\right)$.
      \vspace{2cm}
      \subpart[2] Find $P\left(\text{"an even number is rolled"}\right)$.
      \vspace{2cm}
      \subpart[2] Find $P\left(\text{"an even number is rolled"|"the roll was less than 3"}\right)$.
      \vspace{2cm}
      \subpart[2] Find $P\left(\text{"The coin toss resulted in heads" | "the die roll was less than 3"}\right)$
      \vspace{2cm}
  \end{subparts}

\end{parts}

\newpage

\question

   \begin{parts}
      \part[4] Suppose $X \sim \text{Binom}(4,.2)$. Find $P(X = 3)$.
      \vspace{4cm}
      \part[4] Suppose $Y \sim \text{Geometric}(.9)$. Find $P(Y \ge 10)$.
      \vspace{4cm}
      \part[4] Suppose $M \sim \text{Geometric}(.2)$. Find $P(M \ge 3|M \le 5)$.
      \vspace{4cm}
      \part[4] Using what you know about probability mass functions, evaluate the sum \[ \sum_{k=0}^{\infty} \left(\frac{2}{3}\right)^k \]
      \vspace{4cm}
      \part[4] Suppose that $T$ is an exponential random variable with density function $f(t) = 1.2 e^{-1.2 t}$ with $ t \ge 0$. Sketch the cumulative distribution for $T$. Use it to illustrate the probability of $T$ being less than 4.
      \vspace{4cm}
      \part[4] Suppose that $T$ is an exponential as in the previous part. If we know that $T$ is greater than $5$, what is the probability that $T$ is less than 10?
      \vspace{4cm}
      \part[4] Suppose $R \sim \text{Beta}(3,4)$. Find $P(R \ge .5 | R \ge .2)$.
      \vspace{4cm}
      \part[4] Using what you know about probability density functions, evaluate the integral \[ \int_{-\infty}^{\infty} e^{-2 x^2} dx \]
      \vspace{4cm}
   \end{parts}

\newpage
\question 

Suppose that $X$ is a continuous random variable with probability density function (pdf):
$$
f(x) = 
\begin{cases}
   3 e^{-6x} & x < 0 \\
   3 e^{-6x} & x \ge 0
\end{cases}
$$

We refer to such a random variable as a mirrored exponential random variable.

\begin{parts}
   \part Provide a sketch of the probability density function, $f(x)$.
   \vspace{4cm}
   \part Show that $f(x)$ is a valid pdf.
   \vspace{2cm}
   \part What is the probability that $X$ takes a value greater than 3?
   \vspace{2cm}
   \part What is the probability that $X$ takes a value between -3 and 3?
   \vspace{2cm}
   \part Derive the cumulative density function, $F(x)$ (consider writing it as a piecewise function).
\end{parts}

\end{questions}

\end{document}
